Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-04-29 awipev-CO2.Rmd
Blabla

ggplotRegression <- function(fit){
ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", se= FALSE) +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5)))
}
```

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  # dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
  #        AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
  #        #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
  #        #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
  #        ) %>%
  # variables passed through despike with "-filtered" have been renamed without sufix.
  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, ph_dur = ph_dur_filtered)
d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))

>>>>

ggplotRegression <- function(fit){
ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", se= FALSE) +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5)))
}
```
#blabla
```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  # dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
  #        AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
  #        #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
  #        #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
  #        ) %>%
  # variables passed through despike with "-filtered" have been renamed without sufix.
  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, ph_dur = ph_dur_filtered)
d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))
